Project Notes - Solution Descriptions

### 2020-02-17 StateOfPractice/Peter-Notes-QualityMeasurement.tex
peter's notes - added portability measures; updated first 6 solutions in excel file

Input Variabilities
\begin{enumerate}
	\item boundary parameters
	\item dimension
	\item number of velocity directions
\end{enumerate}

\noindent Calculation Variabilities
\begin{enumerate}
	\item computational model
	\item decomposition technique
	\item coefficient weights
	\item input check
	\item encoding of output
	\item exception check
\end{enumerate}

\noindent Other Variabilities
\begin{enumerate}
	\item language
	\item license
\end{enumerate}

@@

~\newpage
\subsection{Portability}
\subsubsection{Definition}
Effort required to transfer a program between system environments (including hardware and software).\\
\subsubsection{Metrics}
Same as installability?
\begin{enumerate}
	\item Time to port
	\item OS platforms
	\item OS versions
	\item Hardware platforms
	\item Number of external libraries needed
\end{enumerate}

>>>>

\begin{enumerate}
	\item category
	\item dimensions
	\item computational model
	\item decomposition technique
	\item input check
	\item encoding of output
	\item exception check
	\item language
	\item license
	\item parallel
	\item open source
	\item output model
	\item turbulent
	\item complex geometry
	\item non-Newtonian fluids
	\item dependencies
\end{enumerate}

@@

~\newpage
\subsection{Portability}
\subsubsection{Definition}
Effort required to transfer a program between system environments (including hardware and software).\\
\subsubsection{Metrics}
Same as installability?
\begin{enumerate}
	\item OS platforms\\

	Measure the average time (or steps taken) to port the program between a list of OS environments.
	\item OS versions\\

	Measure the average time (or steps taken) to port the program between a list of OS versions.
	\item Hardware platforms\\

	Measure the average time (or steps taken) to port the program between a list of hardware platforms.

	\item Number of external libraries needed\\

	Count the number of external libraries needed to set up the environment.

\end{enumerate}

### 2020-02-17 StateOfPractice/Peter-Notes-SolutionDescriptions.tex
peter's notes - added portability measures; updated first 6 solutions in excel file

	\item ch4-project\\
	\href{https://github.com/ecalzavarini/ch4-project}{https://github.com/ecalzavarini/ch4-project}\\  
	Found using Google search.\\
	Eulerian-Lagrangian fluid dynamics platform
	A general purpose Lattice-Boltzmann code for fluid-dynamics simulations. It includes :
	fluid dynamics (with several volume forcing terms for Channel flow, Homogeneous Isotropic Turbulence, buoyancy)
	temperature dynamics (advection, diffusion , sink/source or reaction terms)
	phase change (enthalpy formulation for solid/liquid systems)
	scalar transport (same functionalities as temperature)
	lagrangian dynamics (tracers, heavy/light and active point-like particles; non-shperical Jeffery rotation, gyrotaxis)
	large eddy simulation (Smagorinsky, Shear Improved Samgorinsky with Kalman Filter)

>>>>

	\item ch4-project\\
	\href{https://github.com/SoftwareImpacts/SIMPAC-2019-1}{https://github.com/SoftwareImpacts/SIMPAC-2019-1}\\  
	Found using Google search.\\
	Eulerian-Lagrangian fluid dynamics platform
	A general purpose Lattice-Boltzmann code for fluid-dynamics simulations. It includes :
	fluid dynamics (with several volume forcing terms for Channel flow, Homogeneous Isotropic Turbulence, buoyancy)
	temperature dynamics (advection, diffusion , sink/source or reaction terms)
	phase change (enthalpy formulation for solid/liquid systems)
	scalar transport (same functionalities as temperature)
	lagrangian dynamics (tracers, heavy/light and active point-like particles; non-shperical Jeffery rotation, gyrotaxis)
	large eddy simulation (Smagorinsky, Shear Improved Samgorinsky with Kalman Filter)
